\Huge ACM and Climate Change

### 2018-12-11 main.tex
Small polishing and responses to Mike

Why ACM? Because one of ACM’s main activities is organizing international
conferences, and these produce significant emissions of greenhouse gases,
particularly from air travel. For example, a single round-trip flight from
Philadelphia to Paris emits the equivalent of about 1.7 tons of carbon dioxide
(\COtwoE) per passenger.\mwh{Cite the carboncalculator.org site I used
  to calculate this?} Compare this against the fact that the average US
resident emits about 16.5 tons per year, while the average European emits
about 7 tons~\cite{emissions}.  Moreover, these emissions have no near-term
technological fix because jet fuel is difficult to replace with renewable
energy sources~\cite{elec-air}. So reducing the \COtwoE{} footprint of conferences is going
to require a reduction in the footprint of the attendees’ air travel.

@@

Another natural idea is to co-locate or consolidate conferences.  This is
already standard practice in some communities---e.g., SIGGRAPH, SC, and CVPR
are all ``the'' conference for their areas.  More communities---for example,
the programming languages and security communities, each of which holds four
main conferences every year---could consider following suit.  A different
twist on this idea would be to hold a single conference in two locations
simultaneously (e.g., Boston and Paris), with a video link between the
sites. Switching to virtual program committee meetings for conferences is
another obvious step. \mwh{data about surprising connection to
  conference's overall footprint?}  Indeed, this switch is already happening: we found in
a recent poll of ACM SIG chairs that, across ACM, a majority of the SIGs’
main conferences now use online PC meetings rather than in-person ones.

We can attend some conferences online, saving both emissions and travel
time.  Indeed, SIGPLAN already livestreams all its four main conferences,
while SIGACCESS and SIGCHI have experimented with telepresence robots at
their main conferences~\cite{CHI-remote,Neustaedter}. Journal-first
initiatives, which make conference attendance optional, could also help.
Looking further ahead, some communities are already experimenting with fully
virtual \mwh{reality?} conferences~\cite{OS}.  ACM members can contribute to the
development of technologies for connecting people effectively at a distance.

Each of these strategies will have some beneficial effect on emissions.  
Each may also have downsides. For example, locating conferences
near their existing ``centers of mass'' may discourage holding them in
countries like India and China where the community is still developing,
while virtual PC meetings and remote conference attendance may reduce
opportunities for informal connections and mentoring.  Getting beyond easy,
short-term solutions will require balancing competing concerns, demanding
discussion, compromise, careful analysis of data, and creative
experimentation.  
%
\bcp{Added remainder of paragraph.  I don't think the two sentences work
together very well, but I can't decide which to keep!}
It will also require questioning some fundamental assumptions about how
research gets done---e.g., that more and bigger conferences are better, and
that personal success is (positively) correlated with time spent in
airports.
%
And to thrive in the long term, we need to begin imagining what a
zero-carbon professional society will look like.

>>>>

Why ACM? Because one of ACM’s main activities is organizing international
conferences, and these produce significant emissions of greenhouse gases,
particularly from air travel. For example, a single round-trip flight from
Philadelphia to Paris emits the equivalent of about 1.7 tons of carbon
dioxide (\COtwoE) per passenger~\cite{carboncalculator}.\iflater\bcp{Trim
  citation?}\fi{} Compare this against the fact that the average US resident
emits about 16.5 tons per year, while the average European emits about 7
tons~\cite{emissions}.  Moreover, these emissions have no near-term
technological fix because jet fuel is difficult to replace with renewable
energy sources~\cite{elec-air}. So reducing the \COtwoE{} footprint of
conferences is going to require a reduction in the footprint of the
attendees’ air travel.

@@

Another natural idea is to co-locate or consolidate conferences.  This is
already standard practice in some communities---e.g., SIGGRAPH, SC, and CVPR
are all ``the'' conference for their areas.  More communities---for example,
the programming languages and security communities, each of which holds four
main conferences every year---could consider following suit.  A different
twist on this idea would be to hold a single conference in two locations
simultaneously (e.g., Boston and Paris), with a video link between the
sites. Switching to virtual program committee meetings for conferences is
another obvious step. \mwh{data about surprising connection to conference's
  overall footprint?}\bcp{Or leave it for next round of revisions when we
  may have done more/better analysis?}  Indeed, this switch is already
happening: we found in a recent poll of ACM SIG chairs that, across ACM, a
majority of the SIGs’ main conferences now use online PC meetings rather
than in-person ones.

We can attend some conferences online, saving both emissions and travel
time.  Indeed, SIGPLAN already livestreams all its four main conferences,
while SIGACCESS and SIGCHI have experimented with telepresence robots at
their main conferences~\cite{CHI-remote,Neustaedter}. Journal-first
initiatives, which make conference attendance optional, could also help.
Looking further ahead, some communities are already experimenting with fully
virtual 
% \mwh{reality?}
% BCP: Seems redundant with "fully"
conferences~\cite{OS}.  ACM members can contribute to the
development of technologies for connecting people effectively at a distance.

Each of these strategies will have some beneficial effect on emissions.  
Each may also have downsides. For example, locating conferences
near their existing ``centers of mass'' may discourage holding them in
countries like India and China where the community is still developing,
while virtual PC meetings and remote conference attendance may reduce
opportunities for informal connections and mentoring.  Getting beyond easy,
short-term solutions will require balancing competing concerns, demanding
discussion, compromise, careful analysis of data, and creative
experimentation.  
%
\bcp{Added remainder of paragraph.  I'm not sure the two sentences work
  together very well, but I can't decide which to keep!  (Mike likes them
  both.)}%
It will also require questioning some fundamental assumptions about how
research gets done---e.g., that more and bigger conferences are better, and
that personal success is (positively) correlated with time spent in
airports.
%
To thrive over the long haul, we need to begin imagining what a zero-carbon
professional society will look like.
